An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-01 VLDB2026/main.tex
Update main.tex
change
Merge remote changes

\title{An Experimental Evaluation of Hybrid Search Algorithms (EA\&B)}

@@

Nearest Neighbor (NN) search \cite{cover1967nearest} aims to find the closest vector in a given space and serves as a fundamental algorithm in vector retrieval, with widespread applications in recommendation systems  \cite{monolith, Airbnb, Related_Pins_at_Pinterest, wang2018billion, pal2020pinnersage, okura2017embedding}  and image retrieval \cite{wang2012scalable}.
% 需要添加引用，下面这段
However, with the exponential growth of data volume and the increasing dimensionality of vectors \cite{weber1998quantitative}, traditional NN search methods struggle to meet the demands of real-time search. To address this issue, researchers turn to more efficient approaches - Approximate NN search ~\cite{arya1998optimal,beis1997shape,gionis1999similarity,malkov2018efficient}. ANN algorithms significantly improve search efficiency by constructing effective indexing structures, albeit at the cost of reduced accuracy.

@@

\begin{figure*}
    \centering
%    \setlength{\abovecaptionskip}{0cm}
%    \setlength{\belowcaptionskip}{-0.4cm}
    \includegraphics[width=\textwidth]{figures/hybrid ANNS.pdf}
    \caption{Hybrid query example}

@@

%    \setlength{\abovecaptionskip}{0cm}
%    \setlength{\belowcaptionskip}{0.2cm}
    \caption{Graph index and IVF index}

@@

\setlength{\textfloatsep}{0cm}
\setlength{\floatsep}{0cm}
\begin{table*}[t]
	\centering
        %\setlength{\belowcaptionskip}{-0.3cm}

	\caption{Comparison of AF-ANN search algorithms}
	\small
	\label{tab:compair_1}
    \begin{tabular}{|l|l|c|c|c|c|c|c|c|}
		\hline
        \textbf{Algorithm} & \textbf{Base} & \textbf{Filter Type} & \textbf{AND} & \textbf{OR} & \textbf{Flexible Attributes} & \textbf{Complex Boolean} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
		\hline
         NHQ & Graph & C & Y & N& N& N & N & N \\
         FilteredVamana & Graph & C & N & Y & Y & N & Y & Y \\
	StitchedVamana & Graph & C & N & Y & Y & N & N & Y  \\
        CAPS & IVF & C & Y & N & N & N & Y & Y \\
        ACORN & Graph & C & Y & Y & Y & Y & Y & Y \\
       UNG & Graph & B & Y & Y & Y & N & Y & Y \\ 
        Puck & IVF & B & Y & Y & Y & N & Y & Y \\
        % ParlayANN & Graph+IVF & B & N & N & Y & N & N & Y \\

		\hline
	\end{tabular}

	\centering
    \footnotesize{
	\begin{minipage}{\linewidth}
		\textsuperscript{A} Post-filtering, 
		\textsuperscript{B} Pre-filtering, 
		\textsuperscript{C} Simultaneous filtering, 
		\textsuperscript{Y} Support, 
		\textsuperscript{N} Unsupport. 
		\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
		\textit{AND} indicates whether the algorithm supports attribute filtering with AND operations. 
		\textit{OR} indicates whether the algorithm supports attribute filtering with OR operations. 
		\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
		\textit{Complex Boolean} refers to whether the algorithm supports advanced Boolean logic beyond just AND and OR, such as NOT or combinations like (A AND B) OR (C AND NOT D). 
		\textit{Dynamic} indicates whether the algorithm supports the operation of dynamically inserting data points.
	\end{minipage}}

\end{table*}

@@

\setlength{\textfloatsep}{0.1cm}
\setlength{\floatsep}{0cm}
\begin{table}[t]
	\centering
%        \setlength{\abovecaptionskip}{0.05cm}
        %\setlength{\belowcaptionskip}{-0.3cm}
%        \setlength{\textfloatsep}{0cm}
	\caption{Comparison of RF-ANN search algorithms}
	\small	% 只会影响当前组的内容
	\label{tab:range_algo}
    \begin{tabular}{|c|c|c|c|}
		\hline
		\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
		\hline
        DSG & Graph & Y & N \\
        iRange & Graph & N & Y \\
        SeRF & Graph & Y & Y \\
		UNIFY & Graph & Y & Y \\
		WinFilter & Graph & N & Y  \\
		\hline
	\end{tabular}

@@

%4.2.1
\subsubsection{Time and Space overhead of index construction}
% \subsubsection{\textbf{Attribute Filtering}}
\begin{figure}[t]
    \centering
%        \setlength{\abovecaptionskip}{0.3cm}
%        \setlength{\belowcaptionskip}{0cm}

@@

    \begin{subfigure}{\columnwidth}
        \centering
%        \setlength{\abovecaptionskip}{0cm}
%        
%        \setlength{\belowcaptionskip}{-0.3cm}
        \includegraphics[width=\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
        \caption{Index construction time}
        \label{fig:build_time_comparison_query1}
    \end{subfigure}

    \begin{subfigure}{\columnwidth}
        \centering
%        \setlength{\abovecaptionskip}{0cm}
%        \setlength{\belowcaptionskip}{-0.3cm}
        \includegraphics[width=\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
        \caption{Index size}
        \label{fig:index_size_mb_comparison_query1}
    \end{subfigure}

    \begin{subfigure}{\columnwidth}
        \centering
%        \setlength{\abovecaptionskip}{0cm}
%        \setlength{\belowcaptionskip}{-0.3cm}
        \includegraphics[width=\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
        \caption{Peak memory usage}
        \label{fig:memory_mb_comparison_query1}
    \end{subfigure}

@@

\begin{figure}[th]
    \centering
%    \setlength{\abovecaptionskip}{0cm}
%    \setlength{\belowcaptionskip}{-0.1cm}
    % 上面的图例，居中并可通过 hspace 调整左右位置
    \hspace*{15pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
    \includegraphics[width=0.98\columnwidth]{figures/exp/exp_2_legend.pdf} % 图例图片路径

@@

\begin{figure*}
        \centering
%        \setlength{\abovecaptionskip}{0cm}
%        \setlength{\belowcaptionskip}{-0.4cm}
        \includegraphics[width=\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
        \caption{Multi-attribute build and query (single thread)}
        \label{fig:exp_4_1_MultiLabel_1thread}
\end{figure*}

\begin{figure*}
        \centering
%        \setlength{\abovecaptionskip}{0cm}
%        \setlength{\belowcaptionskip}{-0.4cm}
        \includegraphics[width=\textwidth]{figures/exp/exp_3_1.pdf}
        \caption{Effect of attribute distribution on query performance (single thread)}
        \label{fig:exp_3_1}
\end{figure*}

@@

\begin{figure}
    \centering
%    \setlength{\abovecaptionskip}{0cm}
%    \setlength{\belowcaptionskip}{-0.1cm}
    \includegraphics[width=\columnwidth]{figures/exp/exp_5_1_1_SingleLabel_1thread.pdf}
    \caption{Effect of Single-Attribute Selectivity on Query}
    \label{fig:exp_5_1_1_SingleLabel_1thread}
\end{figure}

>>>>

\title{An Experimental Evaluation of Hybrid Vector Search (EA\&B)}

@@

Nearest Neighbor (NN) search \cite{cover1967nearest} aims to find the closest vector in a given space and serves as a fundamental algorithm in vector retrieval, with widespread applications in recommendation systems  \cite{monolith}  and image retrieval \cite{wang2012scalable}.
% 需要添加引用，下面这段
However, with the exponential growth of data volume and the increasing dimensionality of vectors \cite{weber1998quantitative}, traditional NN search methods struggle to meet the demands of real-time search. To address this issue, researchers turn to more efficient approaches - Approximate NN search ~\cite{arya1998optimal,beis1997shape,gionis1999similarity,malkov2018efficient}. ANN algorithms significantly improve search efficiency by constructing effective indexing structures, albeit at the cost of reduced accuracy.

@@

\begin{figure*}
    \centering
    \setlength{\abovecaptionskip}{0.1cm}
    \setlength{\belowcaptionskip}{-0.2cm}
    \includegraphics[width=\textwidth]{figures/hybrid ANNS.pdf}
    \caption{Hybrid query example}

@@

    \setlength{\abovecaptionskip}{0.1cm}
    \setlength{\belowcaptionskip}{0.2cm}
    \caption{Graph index and IVF index}

@@

\setlength{\textfloatsep}{0cm}
\setlength{\floatsep}{0cm}
\begin{table*}[t]
	\centering
        %\setlength{\belowcaptionskip}{-0.3cm}
      \setlength{\abovecaptionskip}{0.1cm}
     \setlength{\belowcaptionskip}{-0.2cm}
	\caption{Comparison of AF-ANN search algorithms}
	\small
	\label{tab:compair_1}
    \begin{tabular}{|l|l|c|c|c|c|c|c|c|}
		\hline
        \textbf{Algorithm} & \textbf{Base} & \textbf{Filter Type} & \textbf{AND} & \textbf{OR} & \textbf{Flexible Attributes} & \textbf{Complex Boolean} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
		\hline
         NHQ & Graph & C & Y & N& N& N & N & N \\
         FilteredVamana & Graph & C & N & Y & Y & N & Y & Y \\
	StitchedVamana & Graph & C & N & Y & Y & N & N & Y  \\
        CAPS & IVF & C & Y & N & N & N & Y & Y \\
        ACORN & Graph & C & Y & Y & Y & Y & Y & Y \\
       UNG & Graph & B & Y & Y & Y & N & Y & Y \\ 
        Puck & IVF & B & Y & Y & Y & N & Y & Y \\
        % ParlayANN & Graph+IVF & B & N & N & Y & N & N & Y \\

		\hline

	\end{tabular}

	\centering
%	 \setlength{\abovecaptionskip}{0cm}
%	\setlength{\belowcaptionskip}{0.1cm}
    \footnotesize{
	\begin{minipage}{\linewidth}
		\vspace{0.1cm}
		\textsuperscript{A} Post-filtering, 
		\textsuperscript{B} Pre-filtering, 
		\textsuperscript{C} Simultaneous filtering, 
		\textsuperscript{Y} Support, 
		\textsuperscript{N} Unsupport. 
		\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
		\textit{AND} indicates whether the algorithm supports attribute filtering with AND operations. 
		\textit{OR} indicates whether the algorithm supports attribute filtering with OR operations. 
		\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
		\textit{Complex Boolean} refers to whether the algorithm supports advanced Boolean logic beyond just AND and OR, such as NOT or combinations like (A AND B) OR (C AND NOT D). 
		\textit{Dynamic} indicates whether the algorithm supports the operation of dynamically inserting data points.
	\end{minipage}}
  \vspace{-0.3cm}
\end{table*}

@@

\setlength{\textfloatsep}{0.1cm}
\setlength{\floatsep}{0cm}
\begin{table}[t]
	\centering
        \setlength{\abovecaptionskip}{0.1cm}
        \setlength{\belowcaptionskip}{-0.1cm}
        \setlength{\textfloatsep}{0.1cm}
	\caption{Comparison of RF-ANN search algorithms}
	\small	% 只会影响当前组的内容
	\label{tab:range_algo}
    \begin{tabular}{|c|c|c|c|}
		\hline
		\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
		\hline
        DSG & Graph & Y & N \\
        iRange & Graph & N & Y \\
        SeRF & Graph & Y & Y \\
		UNIFY & Graph & Y & Y \\
		WinFilter & Graph & N & Y  \\
		\hline
	\end{tabular}

@@

%4.2.1
\subsubsection{Time and Space overhead of index construction}
% \subsubsection{\textbf{Attribute Filtering}}
\begin{figure}[t]
    \centering
        \setlength{\abovecaptionskip}{0.3cm}
        \setlength{\belowcaptionskip}{0cm}

@@

    \begin{subfigure}{\columnwidth}
        \centering
        \setlength{\abovecaptionskip}{0cm}
        \setlength{\belowcaptionskip}{-0.1cm}
        \includegraphics[width=\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
        \caption{Index construction time}
        \label{fig:build_time_comparison_query1}
    \end{subfigure}

    \begin{subfigure}{\columnwidth}
        \centering
        \setlength{\abovecaptionskip}{0cm}
        \setlength{\belowcaptionskip}{-0.1cm}
        \includegraphics[width=\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
        \caption{Index size}
        \label{fig:index_size_mb_comparison_query1}
    \end{subfigure}

    \begin{subfigure}{\columnwidth}
        \centering
        \setlength{\abovecaptionskip}{0cm}
        \setlength{\belowcaptionskip}{-0.1cm}
        \includegraphics[width=\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
        \caption{Peak memory usage}
        \label{fig:memory_mb_comparison_query1}
    \end{subfigure}

@@

\begin{figure}[th]
    \centering
    \setlength{\abovecaptionskip}{0.1cm}
    \setlength{\belowcaptionskip}{-0.1cm}
    % 上面的图例，居中并可通过 hspace 调整左右位置
    \hspace*{15pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
    \includegraphics[width=0.98\columnwidth]{figures/exp/exp_2_legend.pdf} % 图例图片路径

@@

\begin{figure*}
        \centering
        \setlength{\abovecaptionskip}{0.1cm}
        \setlength{\belowcaptionskip}{-0.4cm}
        \includegraphics[width=\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
        \caption{Multi-attribute build and query (single thread)}
        \label{fig:exp_4_1_MultiLabel_1thread}
\end{figure*}

\begin{figure*}
        \centering
\setlength{\abovecaptionskip}{0.1cm}
\setlength{\belowcaptionskip}{-0.4cm}
        \includegraphics[width=\textwidth]{figures/exp/exp_3_1.pdf}
        \caption{Effect of attribute distribution on query performance (single thread)}
        \label{fig:exp_3_1}
\end{figure*}

@@

\begin{figure}
    \centering
    \setlength{\abovecaptionskip}{0.1cm}
    \setlength{\belowcaptionskip}{-0.1cm}
    \includegraphics[width=\columnwidth]{figures/exp/exp_5_1_1_SingleLabel_1thread.pdf}
    \caption{Effect of Single-Attribute Selectivity on Query}
    \label{fig:exp_5_1_1_SingleLabel_1thread}
\end{figure}
